\sys: Property-Guided Program Regeneration\\{\vspace{1em}\large Technical University of Denmark, MSc Thesis {\\\vspace{-1em}} Advisors: Christian Gram Kahlauge and Nikos Vasilakis

### 2025-07-18 docs/paper/draft.tex
Add to discussion
Signed-off-by: Evangelos Lamprou <vagos@lamprou.xyz>

\section{Discussion and Limitations}
\label{sec:discussion}

\sys's design comes with inherent trade-offs.

@@

@@

Here, I outline possible future directions for \sys and its successors:

>>>>

\section{Discussion}
\label{sec:discussion}

\begin{figure}[t]
  % https://docs.google.com/drawings/d/1ozMu2B0RUhyLWC_rM6GLBrioov80-M06CBqYRAhCk18/edit
  \includegraphics[width=.8\columnwidth]{figs/kvasir_projection.pdf}
  \caption{\textbf{Regeneration from property projection.}
  An alternative view of \sys is that instead of transforming source code directly, it projects the original
  program into a set of verifiable properties---such as input/output
  examples, system call traces, \etc.
  It then regenerates it and turns it back into source code.}
  \label{fig:projection}
\end{figure}

This section discusses \sys's inherent trade-offs and possibilities for future work.

@@

\heading{Idea of program projection}
\sys can be viewed as a projection system, as shown in \cref{fig:projection}.
\sys projects a program into an abstract space of properties, 
then, it performs transformations within that space (the input query),
and finally, it regenerates this projection back into a concrete program.
The idea of casting programs into a high-dimensioanl space has been studied before~\cite{ben-nun2018neural,alon2019code2vec,ellis2020dreamcoder,nye2021platypus},
but \sys's approach, from this perspective, might offer interesting insights.

@@
